\documentclass{article}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{enumitem}

\geometry{a4paper, margin=1in}
\setlength{\parindent}{0pt}

\title{Progress Report\\[0.5em]
\large Watch-Log}
\author{Alvin Johns\\
CS463\\
Date: April 19, 2024}
\date{}

\begin{document}

\maketitle

\section*{Individual Tasks}
\subsection*{Completed (in the last seven days)}
\begin{itemize}[label={--}]
    \item Self:
        \begin{itemize}[label={}]
            \item Created a starting binaries for client and server unix sockets.
        \end{itemize}
\end{itemize}

\subsection*{Planned (for the next progress report)}
\begin{itemize}[label={--}]
    \item Self:
        \begin{itemize}[label={}]
            \item Get client error handling working. 
            \item Debug server stderr output when running in the background. 
        \end{itemize}
\end{itemize}

\subsection*{Links to Issues or Pull Requests}
\begin{itemize}[label={--}]
    \item main: \url{https://github.com/endepointe/watch-log}
\end{itemize}

\section*{Meeting Minutes}
\begin{itemize}[label={--}]
    \item Met with Kirsten and discussed the project requirements. Set goal to complete solo project, deliver expo requirements, and present to incoming 362 group about this unique experience. 30 minutes.
\end{itemize}

\section*{Open Questions, Concerns, or Blockers}
\begin{itemize}[label={--}]
    \item Is ebpf still an option with this amount of time left? I hope and I sure will try.
    \item Need new PRD
    \item Need new SDP?
    \item Need new SDA?
    \item Need diagrams and github pages site.
\end{itemize}

\section*{Major Changes in Assets this Week}
\begin{itemize}[label={--}]
    \item Completely new code base. 
\end{itemize}

%\section*{Additional Documents TODO}
%\begin{itemize}[label={--}]
%    \item Product Requirements Document: \url{link}
%    \item Software Development Process: \url{link}
%    \item Software Design and Architecture: \url{link}
%    \item Product Design, User Persona, User Research, etc.: \url{link}
%    \item Documentation: \url{link}
%\end{itemize}

\end{document}

